Token-level author diarization using clustering of stylistic contexts

### 2017-06-02 paper/paper.tex
no message

In task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set. Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results. Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering. Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set. We measured macro $F_\mathrm{M}$.

@@

We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.

The results of evaluation for the intrinsic plagiarism problem (task \emph{a}) are shown in table \ref{tab:results-task-a}. For author diarization with known (task \emph{b}) and unknown (task \emph{c}) numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.

\subsection{Intrinsic plagiarism detection results}

@@

@@

\subsection{Author diarization results}

\begin{table*}
	\caption{Results on the author diarization task.}
	\label{tab:results-task-b-c}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

>>>>

In task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set. Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results. Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering. Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set. We measured macro-averaged $F_1$-score.

@@

We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}. The results of our models are compared to the reuslts of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem. The results of the two teams have been evaluated on test sets that is not publicly available. Only the training sets from the competition have been available to us.

The results of evaluation for the intrinsic plagiarism problem are shown in table \ref{tab:results-task-a}. For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.

{Intrinsic plagiarism detection results}

@@

{Author diarization results}

@@

\begin{table*}
	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.}
	\label{tab:results-task-b-c}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
			\cmidrule{2-7}
			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
			\midrule
			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
			\midrule
			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
			\midrule			
			Model A 					&  &  &  &  &  & \\			
			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}
